---
title: "SQL Tables"
output: slidy_presentation
runtime: shiny
css: complex-css.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r load dataset2.RData, echo=FALSE}
tmpenv <- new.env()
load("/Users/georgiosmartakis/Downloads/my_data/ACRER/data/dataset1.rda", envir = tmpenv)
dataset1 <- tmpenv$dataset1
```
```{r shiny_app, echo=FALSE}
library(shiny)

shinyApp(shinyUI <- pageWithSidebar(
  # Application title
  headerPanel("Original Tables used for queries"),

    sidebarPanel(
    tags$style(HTML('body {font-family:"Times New Roman",Georgia,Serif; background-color:white}')),
    tags$style(HTML('#textInput {font-family:"surabanglus",Georgia,Serif; background-color:lightblue}')),
    textInput("caption", "Caption:", "Data Summary"),
    selectInput("dataset1", "Choose a dataset:", 
                choices = c("Table_2_RecrID_type_coordinates_prices","Table_3_RecrID_type_activity_pattern","Table_5_activities_definition_costs","Table_14_hgpID_groups_types","Table_16_hgpID_min_max_budgets","Table_7_zip_hgpID_budget","Table_9_zip_code_RecrID_distances","Table_8_hgpID_distance_costs","Table_10_hgpID_activity_budget","Time_segment_selected","zip_code_coordinates")),numericInput("obs", "Number of observations to view:", 50)
),
  mainPanel(
    h1(textOutput("Caption")),
    #    verbatimTextOutput(outputId = "summary", placeholder = TRUE),
    tableOutput("view")
  )
),
shinyServer <- function(input, output) {
# By declaring datasetInput as a reactive expression we ensure that:
#  1) It is only called when the inputs it depends on changes
#  2) The computation and result are shared by all the callers (it
#     only executes a single time)

  datasetInput <- reactive({
    switch(input$dataset1,
          "Table_2_RecrID_type_coordinates_prices" = dataset1[[1]],
          "Table_3_RecrID_type_activity_pattern" = dataset1[[2]],
          "Table_5_activities_definition_costs" = dataset1[[3]],
          "Table_14_hgpID_groups_types" = dataset1[[4]],
          "Table_16_hgpID_min_max_budgets" = dataset1[[5]],
          "Table_7_zip_hgpID_budget" = dataset1[[6]],
          "Table_9_zip_code_RecrID_distances" = dataset1[[7]],
          "Table_8_hgpID_distance_costs" = dataset1[[8]],
          "Table_10_hgpID_activity_budget" = dataset1[[9]],
          "Time_segment_selected" = dataset1[[10]],
          "zip_code_coordinates" = dataset1[[11]])
  })
  
  output$summary <- renderPrint({
    dataset <- datasetInput()
    summary(dataset1)
  })
  output$view <- renderTable({
    head(datasetInput(), n = input$obs)
  })
}
)
