---
title: "SQL Tables"
output: slidy_presentation
runtime: shiny
css: complex-css.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r load dataset2.RData, echo=FALSE}
tmpenv <- new.env()
load("dataset2.RData", envir = tmpenv)
dataset2 <- tmpenv$dataset2
```
```{r shiny_app, echo=FALSE}
library(shiny)
library(shinythemes)


shinyApp(shinyUI <- fluidPage(theme = shinytheme("superhero"),
  
  # Application title
  titlePanel("Tables created by sql queries "),

  sidebarLayout( 

        sidebarPanel(
               textInput("caption", "Caption:", "Data Summary"),
               selectInput("dataset2", "Choose a dataset:",
               choices = c("Final_table","data","ActInfo","TimeInfo")),
               numericInput("obs", "Number of observations to view:", 1000),
               width = 3
        ),
        mainPanel(
            h3(textOutput("Caption")),
            tableOutput("view")
        ),
      )
   ),
shinyServer <- function(input, output) {
  
  # By declaring datasetInput as a reactive expression we ensure that:
  #
  #  1) It is only called when the inputs it depends on changes
  #  2) The computation and result are shared by all the callers (it
  #     only executes a single time)
  #
  datasetInput <- reactive({
    switch(input$dataset2,
           "Final_table" = dataset2[[1]],
           "data" = dataset2[[2]],
           "ActInfo" = dataset2[[3]],
           "TimeInfo" = dataset2[[4]])
  })
  
  # The output$summary depends on the datasetInput reactive expression,
  # so will be re-executed whenever datasetInput is invalidated
  # (i.e. whenever the input$dataset changes)
  output$summary <- renderPrint({
    dataset <- datasetInput()
    summary(dataset2)
  })
  # Define server logic required to summarize and view the selected dataset
  # The output$view depends on both the databaseInput reactive expression
  # and input$obs, so will be re-executed whenever input$dataset or
  # input$obs is changed.
  output$view <- renderTable({
    head(datasetInput(), n = input$obs)
  })
}
)
